Numerical investigation of low-load operation of a subcritical power boiler using CFD and process modelling

### 2021-10-05 PAPER_2/PAPER_2_REV1.tex
Update1 - 05/10/2021
Update2 - 05/10/2021

\journal{Journal of Applied Thermal Engineering}

@@

\title{Numerical investigation of the low-load operating protocol of a 620MWe sub-critical power boiler through co-simulation}

%% Group authors per affiliation:
\author{B.T. Rawlins}
\author{R. Laubscher\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{ryno.laubscher@uct.ac.za}
\author{P. Rousseau}
\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modeling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}

@@

The use of coal fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change. However, the switch to more sustainable generation sources pose great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}. The promising integration of renewable energy and the decommissioning of old CFPPs in South Africa, will push CFPP from a primarily base load operation to a mid-merit/flexible operating protocol. This will inherently mean CFPPs will need to operate at low-loads for continuous time periods.

Mathematical models that can accurately capture the behaviour of the boilers thermal-hydraulic response at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Since, the long term deviation from design conditions can lead to operational incapabilities affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.

The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumnavigating the use of time-consuming and costly field tests. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).

@@

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 \%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions. However, to the best the authors' knowledge, no integration of 1-D thermal-hydraulic model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.

The use of a 1-D thermal-hydraulic modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually used to investigate a transient event, such as a sudden disturbance, start-up or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D thermal-hydraulic models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.

The use of coupled simulations has proven to solve the deficiencies of a full 1-D thermal-hydraulic model by coupling the fireside CFD to a 1-D water network. Recently Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}. Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.

The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler. Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $[^\circ C]$.

@@

\section{Mathematical model}
In this section the modelling techniques used by the study are elaborated. A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport field resolution. Following this is a description of the heat transfer modelling techniques and the ends with a description of the process modelling configuration.
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}
To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density is defined present as follows;
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

In the present study the realizable k-$\epsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally generates higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.

The process of coal combustion comprises four steps. Namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions. Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
\begin{gather}
\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
\begin{split}
&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
\end{split}
\end{gather}

A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized. The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a multi-phase Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy.The pseudo particles transported into the domain are modelled using the general scalar field transport equation \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash. Each of the scalar field equations are given in Table \ref{tab_scalars}.

@@

The energy transport of the pseudo particle, is transported by defining the particle enthalpy using the following equation:
\begin{equation}\label{eqn_phi_hp}
\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg}\right)\frac{1}{V}
\end{equation}

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic.

\subsection{Heat transfer modelling modelling}
The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}
In the present work the RTE is solved sing the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

The flue gas absorptivity was calculated using the domain based weighted sum of gray gas model (WSGGM) using the coefficients determined by Smith et al \cite{Smith1982}. The WSGGM accounts for the radiation emitted by tri-atomic gases, namely $CO_2$, $H_2O$ and $SO_2$ present in the flue gas stream. The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p = \rho \phi_{mp0} V / \left( \rho_p \pi \bar{d_p}^3 /6 \right)$) present in a cell. There formulations are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
\begin{gather}
\alpha_p = \frac{\epsilon_p A_{pn}N_p}{V} \label{eqn_part_abs}\\
\sigma_p = \frac{(1-\epsilon_p)(1-f_p) A_{pn}N_p}{V} \label{eqn_part_scat} \\
E_p = \frac{\epsilon_p \sigma_{SB} T_p^4 A_{pn}N_p}{V}\label{eqn_part_emisp}
\end{gather}

@@

\subsection{Process simulation model}
A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchanging components was developed using Flownex SE\textsuperscript{\textregistered} 2021. The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls. The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit. The heat exchangers were modelled using a two-phase mixture approach, this assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area. The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
\begin{gather}
\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
\end{gather}
Applying the mixture density the following transport equations are solved;

@@

The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case. The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various cases have on the system.

\section{Case study boiler description \& set-up}
In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boilers geometry, the process model set-up, the various  modelling inputs (i.e. fuel characteristics and boundary conditions) and ends with the numerical solution strategy.

@@

The boiler furnace is fed by 6 mills, each supplying a pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners. This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.

The process model of the boiler configuration is shown in Figure \ref{fig_flownex}. The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH). The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.5]{FLOWNEX_SETUP}
\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
\label{fig_flownex}
\end{figure}

>>>>

\journal{Energy}

@@

\title{Numerical investigation of low-load operation of a subcritical power boiler using CFD and process modelling}

%% Group authors per affiliation:
\author{B.T. Rawlins}
\author{R. Laubscher\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{ryno.laubscher@uct.ac.za}
\author{P. Rousseau}
\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modeling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
\address{$^*$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}

@@

The use of coal-fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change. However, the switch to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resource present in Southern Africa, CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}. The promising integration of renewable energy and the decommissioning of old CFPPs in Southern Africa, will push these plants from a primarily base load operation to a mid-merit/flexible operating protocol. The switch to flexible operation will inherently mean CFPPs will need to operate at low-loads for continuous time periods.

Mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Since, the long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.

The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumventing the use of time-consuming and costly field tests. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).

@@

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 \%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions. The aforementioned reseacrh specifically investigated combustion and gas-side effects. However, to the best the authors' knowledge, no integration of 1-D process model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.

The use of a 1-D process modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually used to investigate a transient event, such as a sudden disturbance, start-up or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Some recent papers that investigated boiler operations using a co-simulation approach are: Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}. Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.

The goal of the current work is to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flow-rates and metal temperatures. The current work proposes the use of CFD modelling  to investigate the low-load gas-side effects at various firing conditions for a 620 $MWe$ two-pass sub-critical boiler. For the current work CFD gas-side results are coupled to a comprehensive process model of the case study boilers water side.

@@

\section{Mathematical model}
In this section the modelling techniques used by the study are briefly discussed.
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}
To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows;
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

In the present study the realizable k-$\epsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.

The process of coal combustion comprises of four sequential steps. Namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions. Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
\begin{gather}
\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
\begin{split}
&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
\end{split}
\end{gather}

A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study. The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash. Each of the scalar field equations are given in Table \ref{tab_scalars}.

@@

The energy transport of the pseudo particle phase, is transported by defining a particle phase energy equation, which in turn uses the particle enthalpy.
\begin{equation}\label{eqn_phi_hp}
\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg}\right)\frac{1}{V}
\end{equation}

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. To solve the additional transport equations and their source terms, C programs were developed.

\subsection{Heat transfer modelling modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}
In the present work the RTE is solved using the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

The flue gas absorptivity was calculated using the domain based weighted sum of gray gas model (WSGGM) using the coefficients determined by Smith et al \cite{Smith1982}. The WSGGM accounts for the radiation emitted by tri-atomic gases, namely $CO_2$, $H_2O$ and $SO_2$ present in the flue gas stream. The Eulerian description of the terms $\alpha_p$, $\sigma_p$ and $E_b$ are determined using the effective number of particles ($N_p = \rho \phi_{mp0} V / \left( \rho_p \pi \bar{d_p}^3 /6 \right)$) present in a cell. The equations for the radiative properties are given in equations (\ref{eqn_part_abs}) through (\ref{eqn_part_emisp}).
\begin{gather}
\alpha_p = \frac{\epsilon_p A_{pn}N_p}{V} \label{eqn_part_abs}\\
\sigma_p = \frac{(1-\epsilon_p)(1-f_p) A_{pn}N_p}{V} \label{eqn_part_scat} \\
E_p = \frac{\epsilon_p \sigma_{SB} T_p^4 A_{pn}N_p}{V}\label{eqn_part_emisp}
\end{gather}

@@

\subsection{Process simulation model}
A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021. The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls. The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit. The heat exchangers were modelled using a two-phase mixture approach, this assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area. The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
\begin{gather}
\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
\end{gather}
Applying the mixture density the following transport equations are solved per process model component;

@@

The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case. The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various Cases have on the water-side of the boiler system.

\section{Case study boiler description \& set-up}
In this section the numerical model configuration, for both the CFD and process model, will be explained, covering the boiler geometry, the process model set-up, the various  modelling inputs (i.e. fuel characteristics and boundary conditions) and the numerical solution strategy.

@@

The boiler furnace is fed by 6 mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners. This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.

The process model of the boiler configuration is shown in Figure \ref{fig_flownex}. The process model includes all the heat exchangers up to and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH). The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets. The process model is used to determine the required attemperation flow-rates and water/steam side thermal response. The furnace water-walls are represented by a single lumped pipe flow component and forms part of the natural circulation system which include the downcomers and steam drum. As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.

The coupling interface between the simulation models are the heat exchanger external tube surfaces, namely the furnace, platen and final SH walls. The CFD heat loads are used as energy sources for these components as indicated in Figure \ref{fig_flownex}. Furthermore, the CFD flue-gas results (i.e. composition, mass flow and temperature) exiting the final SH are used as boundary inputs for the heat exchangers downstream of the final SH (SH3). The steam flow boundary values for the RH and EC sections are fixed mass inlet flows and temperatures with the corresponding outlets set to a fixed pressure.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.5]{FLOWNEX_SETUP}
\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
\label{fig_flownex}
\end{figure}

\newpage
\subsection{Model inputs}
Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the fuels higher heating value (HHV).\\
\begin{table}[h!]
\centering
\caption{Utility boiler fuel characteristics}
\vspace{2mm}
\label{tbl_fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.3\textwidth} l}
\hline
\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
\hline
\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
Carbon & $0.7753$ & $kg/kg_{fuel}$\\
Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
Ash & $0.4090$ & $kg/kg_{fuel}$\\
Moisture & $0.0550$ & $kg/kg_{fuel}$\\
\hline
\textbf{Energy content - (DAF)} & \textbf{Value} &\\
\hline
Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
\hline
\end{tabularx}}
\end{table}

For a 32 \% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.  For this study six Cases are simulated in total with the following three burner firing configurations being investigated:
\begin{enumerate}
\item Bottom front and rear row burners are fired (Case 1 \& Case 4)
\item Middle front and rear row burners are fired (Case 2 \& Case 5)
\item Bottom front and middle rear row burners are fired (Case 3 \& Case 6)
\end{enumerate}
